### 2021-06-08 figures/results/tables/student_infections_table.tex
List of bullets for report for Science, first draft.
Add current result figures and tables.
Add new results figures.
New results.

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             843318 \\
 educ open after easter  with tests    &                                             607352 \\
 baseline                              &                                             479015 \\
 close educ after easter               &                                             475397 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             752932 \\
 educ open after easter  with tests    &                                             583570 \\
 close educ after easter               &                                             443978 \\
 baseline                              &                                             459436 \\
\bottomrule
\end{tabular}

### 2021-06-08 paper/model_validation.tex
Address some of HM's comments.

% Despite fitting only four infection probabilities, the in-sample fit is very good.
% The best fit is achieved in the largest age groups.
% This is so mechanically, because we weigh the
% deviations between simulated and observed infection rates by group sizes. The worst fit
% is achieved for the 80 to 100 years old.
% There are three reasons for this: Firstly, we only model private households at
% the moment, meaning that nursing homes are not part of the synthetic population we
% simulate. Since community housing residents are part of the German Mikrozensus
% \citep{FDSAeDBUDL2018} which forms the basis for our synthetic population, we can and
% plan to include community housing residents in the near future.
% Secondly, the elderly, especially nursing home residents, are tested more often than
% the general population leading to more cases being detected in this age group.
% We are currently working to include age-variant testing strategies,
% using \href{https://ars.rki.de/Content/COVID19/Main.aspx}{data by the RKI}
% \citep{Seifried2020}.

@@

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/out_of_sample_validation}
    \caption{Predicted effect of the "Lockdown Light" on infection rates.}
    \label{fig:out-of-sample-fit}
    \figurenotes{
        For the time period until the beginning of November, the figure shows the weekly
        incidence rates of infections per 100,000 people from reported (black) versus
        simulated (blue) data. With the start of November, the projections of the three
        scenarios, optimistic (blue), neutral (red), and pessimistic (mint green), are
        shown until the beginning of the Christmas holidays. The actual incidence rates
        (black) are reported until the 24th November.
    }
\end{figure}

>>>>

% Despite fitting only four infection probabilities, the in-sample fit is very good. The
% best fit is achieved in the largest age groups. This is so mechanically, because we
% weigh the deviations between simulated and observed infection rates by group sizes.
% The worst fit is achieved for the 80 to 100 years old. There are three reasons for
% this: Firstly, we only model private households at the moment, meaning that nursing
% homes are not part of the synthetic population we simulate. Since community housing
% residents are part of the German Mikrozensus \citep{FDSAeDBUDL2018} which forms the
% basis for our synthetic population, we can and plan to include community housing
% residents in the near future. Secondly, the elderly, especially nursing home
% residents, are tested more often than the general population leading to more cases
% being detected in this age group. We are currently working to include age-variant
% testing strategies, using \href{https://ars.rki.de/Content/COVID19/Main.aspx}{data by
% the RKI} \citep{Seifried2020}.

@@

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/out_of_sample_validation}
    \caption{Predicted effect of the "Lockdown Light" on infection rates.}
    \label{fig:out-of-sample-fit}
    \figurenotes{For the time period until the beginning of November, the figure shows
        the weekly incidence rates of infections per 100,000 people from reported
        (black) versus simulated (blue) data. With the start of November, the
        projections of the three scenarios, optimistic (blue), neutral (red), and
        pessimistic (mint green), are shown until the beginning of the Christmas
        holidays. The actual incidence rates (black) are reported until the 24th
        November.}
\end{figure}
